Summary of cell type ontologies in reference files

### 2025-08-19 analyses/cell-type-consensus/exploratory-notebooks/06-update-consensus-scimilarity.Rmd
fix some rendering

# for all cell types we want to look at print out a table of the pairs that give rise to that cell type
celltypes_to_explore |> 
  purrr::map(
    \(celltype){
      lca_df |> 
        dplyr::filter(cl_annotation == {{celltype}}) |> 
        dplyr::select(id1_annotation, id2_annotation, total_lca, cl_annotation) |> 
        unique() |> 
        kable()
    }
  )
```

>>>>

# for all cell types we want to look at print out a table of the pairs that give rise to that cell type
celltypes_to_explore |> 
  purrr::map(
    \(celltype){
      lca_df |> 
        dplyr::filter(cl_annotation == {{celltype}}) |> 
        dplyr::select(id1_annotation, id2_annotation, total_lca, cl_annotation) |> 
        unique()
    }
  )
```
